MS_CNuptake.Rmd

### 2022-07-11 MS_CNuptake.Rmd
renamed columns of df returned by rbeni function read_nc_onefile()

###3. calculate weighted-sum
#firstly - filter na points - so that all output map has same numbers of NA.
all_predictors <- as.data.frame(cbind(Tg$myvar,PPFD$myvar,vpd$myvar,
                                      fAPAR$myvar,age$myvar,
                                      CNrt$myvar,LMA$myvar,vcmax25_df$myvar))
all_predictors$available_grid = rowMeans(all_predictors)
#just to find all na columns
all_predictors$available_grid[is.na(all_predictors$available_grid)==FALSE] <- 1
summary(all_predictors$available_grid)
available_grid2 <- all_predictors$available_grid

@@

npp_f <- summary(bp_model)$coefficients[1,1] +  
  summary(bp_model)$coefficients[2,1] * Tg$myvar +
  summary(bp_model)$coefficients[3,1] * fAPAR$myvar +
  summary(bp_model)$coefficients[4,1] * log(PPFD$myvar) +
  summary(bp_model)$coefficients[5,1] * log(CNrt$myvar)+
  summary(bp_model)$coefficients[6,1] * log(age$myvar)

@@

anpp_f <- npp_f * 
  (1/(1 + exp(-(summary(anpp_tnpp_model)$coefficients[1,1]+
                  summary(anpp_tnpp_model)$coefficients[2,1] * log(CNrt$myvar) +
                  summary(anpp_tnpp_model)$coefficients[3,1] * log(PPFD$myvar) + 
                  summary(anpp_tnpp_model)$coefficients[4,1] * Tg$myvar+
                  summary(anpp_tnpp_model)$coefficients[5,1] * log(age$myvar)))))

@@

lnpp_f <- anpp_f * (1/(1 + exp(-(summary(anpp_leafnpp_model)$coefficients[1,1]+
                                   summary(anpp_leafnpp_model)$coefficients[2,1]* fAPAR$myvar +
                                   summary(anpp_leafnpp_model)$coefficients[3,1] * log(vpd$myvar) + 
                                   summary(anpp_leafnpp_model)$coefficients[4,1] * log(PPFD$myvar)))))

@@

leafnc_f <- (summary(n1)$coefficients[1,1]/0.47) + 
  (summary(n1)$coefficients[2,1]/0.47) * vcmax25_df$myvar/LMA$myvar

nre_f <- (1/(1+exp(-(summary(nre_model)$coefficients[1,1] +
                       summary(nre_model)$coefficients[2,1] *Tg$myvar +
                       summary(nre_model)$coefficients[3,1] * log(vpd$myvar)))))

@@

#LMG test in forest
df_all <- (as.data.frame(cbind(nuptake_f,npp_f,all_predictors)))
df_all$nue <- df_all$npp_f/df_all$nuptake_f

@@

#grass
npp_g <- summary(bp_grass_model)$coefficients[1,1] +  
  summary(bp_grass_model)$coefficients[2,1] * log(PPFD$myvar) +
  summary(bp_grass_model)$coefficients[3,1] * Tg$myvar

@@

#work on effect of each factor on NUE
#now, work on NUE
nue_final <- all_maps$NUE # by default
cal_nue <- function(Tg_pred,PPFD_pred,vpd_pred,fAPAR_pred,age_pred,CNrt_pred,LMA_pred,vcmax25_pred){
  npp_f <- summary(bp_model)$coefficients[1,1] +  
    summary(bp_model)$coefficients[2,1] * Tg_pred +
    summary(bp_model)$coefficients[3,1] * fAPAR_pred +
    summary(bp_model)$coefficients[4,1] * log(PPFD_pred) +
    summary(bp_model)$coefficients[5,1] * log(CNrt_pred)+
    summary(bp_model)$coefficients[6,1] * log(age_pred)

@@

nue_standard <- cal_nue(Tg$myvar,PPFD$myvar,vpd$myvar,fAPAR$myvar,
                        age$myvar,CNrt$myvar,LMA$myvar,vcmax25_df$myvar)
summary(nue_standard)

mean_Tg <- mean(Tg$myvar[is.na(available_grid2)==FALSE]);mean_Tg
mean_PPFD <- mean(PPFD$myvar[is.na(available_grid2)==FALSE]);mean_PPFD
mean_vpd <- mean(vpd$myvar[is.na(available_grid2)==FALSE]);mean_vpd
mean_fAPAR <- mean(fAPAR$myvar[is.na(available_grid2)==FALSE]);mean_fAPAR
mean_age <- mean(age$myvar[is.na(available_grid2)==FALSE]);mean_age
mean_CNrt <- mean(CNrt$myvar[is.na(available_grid2)==FALSE]);mean_CNrt
mean_LMA <- mean(LMA$myvar[is.na(available_grid2)==FALSE]);mean_LMA
mean_vcmax25 <- mean(vcmax25_df$myvar[is.na(available_grid2)==FALSE]);mean_vcmax25

nue_Tg <- cal_nue(rep(mean_Tg,259200),PPFD$myvar,vpd$myvar,fAPAR$myvar,age$myvar,CNrt$myvar,LMA$myvar,vcmax25_df$myvar)
nue_PPFD <- cal_nue(Tg$myvar,rep(mean_PPFD,259200),vpd$myvar,fAPAR$myvar,age$myvar,CNrt$myvar,LMA$myvar,vcmax25_df$myvar)
nue_vpd <- cal_nue(Tg$myvar,PPFD$myvar,rep(mean_vpd,259200),fAPAR$myvar,age$myvar,CNrt$myvar,LMA$myvar,vcmax25_df$myvar)
nue_fAPAR <- cal_nue(Tg$myvar,PPFD$myvar,vpd$myvar,rep(mean_fAPAR,259200),age$myvar,CNrt$myvar,LMA$myvar,vcmax25_df$myvar)
nue_age <- cal_nue(Tg$myvar,PPFD$myvar,vpd$myvar,fAPAR$myvar,rep(mean_age,259200),CNrt$myvar,LMA$myvar,vcmax25_df$myvar)
nue_CNrt <- cal_nue(Tg$myvar,PPFD$myvar,vpd$myvar,fAPAR$myvar,age$myvar,rep(mean_CNrt,259200),LMA$myvar,vcmax25_df$myvar)
nue_LMA <- cal_nue(Tg$myvar,PPFD$myvar,vpd$myvar,fAPAR$myvar,age$myvar,CNrt$myvar,rep(mean_LMA,259200),vcmax25_df$myvar)
nue_vcmax25 <- cal_nue(Tg$myvar,PPFD$myvar,vpd$myvar,fAPAR$myvar,age$myvar,CNrt$myvar,LMA$myvar,rep(mean_vcmax25,259200))

@@

# for all logit function model (mod_tnpp, mod_anpp, mod_lnpp, nre_model): a = 1/(1+exp(-b)), where a is the ratio (e.g. npp/gpp) and b is the regression (e.g. mod =tnpp)
#we calculate uncertainty of b firstly, based on each regression
#now we need to calculate deriative a / deriative b, based on a = 1/(1+exp(-b)). After calculation it is: exp(-b) / ( (1 + exp(-b)) ^2)
#forest anpp
mod_anpp_uncertainty <- summary(anpp_tnpp_model)$sigma
anpp_b <- summary(anpp_tnpp_model)$coefficients[1,1]+
  summary(anpp_tnpp_model)$coefficients[2,1] * log(CNrt$myvar) +
  summary(anpp_tnpp_model)$coefficients[3,1] * log(PPFD$myvar) + 
  summary(anpp_tnpp_model)$coefficients[4,1] * Tg$myvar+
  summary(anpp_tnpp_model)$coefficients[5,1] * log(age$myvar)

@@

## Uncertainty of LNPP/ANPP
mod_lnpp_uncertainty <- summary(anpp_leafnpp_model)$sigma
lnpp_b <- summary(anpp_leafnpp_model)$coefficients[1,1]+
  summary(anpp_leafnpp_model)$coefficients[2,1]* fAPAR$myvar +
  summary(anpp_leafnpp_model)$coefficients[3,1] * log(vpd$myvar) + 
  summary(anpp_leafnpp_model)$coefficients[4,1] * log(PPFD$myvar)

@@

#NRE
mod_nre_uncertainty <- summary(nre_model)$sigma
nre_b <- summary(nre_model)$coefficients[1,1]  +
  summary(nre_model)$coefficients[2,1] * Tg$myvar + summary(nre_model)$coefficients[3,1] * log(vpd$myvar)
mod_nre_uncertainty <- mod_nre_uncertainty *  exp(-nre_b) / ( (1 + exp(-nre_b)) ^2)
summary(mod_nre_uncertainty)

>>>>

###3. calculate weighted-sum
#firstly - filter na points - so that all output map has same numbers of NA.
# all_predictors <- as.data.frame(cbind(Tg$Tg,PPFD$PPFD,vpd$vpd,
#                                       fAPAR$fAPAR,age$age,
#                                       CNrt$myvar,LMA$LMA,vcmax25_df$vcmax25))

all_predictors <- as.data.frame(cbind(Tg$Tg, PPFD$PPFD, vpd$vpd,
                                      fAPAR$fAPAR, age$age,
                                      CNrt$CNrt, LMA$LMA, vcmax25_df$vcmax25 ))

all_predictors$available_grid = rowMeans(all_predictors)
#just to find all na columns
all_predictors$available_grid[is.na(all_predictors$available_grid)==FALSE] <- 1
summary(all_predictors$available_grid)
available_grid2 <- all_predictors$available_grid

@@

npp_f <- summary(bp_model)$coefficients[1,1] +  
  summary(bp_model)$coefficients[2,1] * Tg$Tg +
  summary(bp_model)$coefficients[3,1] * fAPAR$fAPAR +
  summary(bp_model)$coefficients[4,1] * log(PPFD$PPFD) +
  summary(bp_model)$coefficients[5,1] * log(CNrt$CNrt)+
  summary(bp_model)$coefficients[6,1] * log(age$age)

@@

anpp_f <- npp_f * 
  (1/(1 + exp(-(summary(anpp_tnpp_model)$coefficients[1,1]+
                  summary(anpp_tnpp_model)$coefficients[2,1] * log(CNrt$CNrt) +
                  summary(anpp_tnpp_model)$coefficients[3,1] * log(PPFD$PPFD) + 
                  summary(anpp_tnpp_model)$coefficients[4,1] * Tg$Tg+
                  summary(anpp_tnpp_model)$coefficients[5,1] * log(age$age)))))

@@

lnpp_f <- anpp_f * (1/(1 + exp(-(summary(anpp_leafnpp_model)$coefficients[1,1]+
                                   summary(anpp_leafnpp_model)$coefficients[2,1]* fAPAR$fAPAR +
                                   summary(anpp_leafnpp_model)$coefficients[3,1] * log(vpd$vpd) + 
                                   summary(anpp_leafnpp_model)$coefficients[4,1] * log(PPFD$PPFD)))))

@@

leafnc_f <- (summary(n1)$coefficients[1,1]/0.47) + 
  (summary(n1)$coefficients[2,1]/0.47) * vcmax25_df$vcmax25/LMA$LMA

nre_f <- (1/(1+exp(-(summary(nre_model)$coefficients[1,1] +
                       summary(nre_model)$coefficients[2,1] *Tg$Tg +
                       summary(nre_model)$coefficients[3,1] * log(vpd$vpd)))))

@@

#LMG test in forest
df_all <- (as.data.frame(cbind(nuptake_f, npp_f, all_predictors)))
df_all$nue <- df_all$npp_f/df_all$nuptake_f

@@

#grass
npp_g <- summary(bp_grass_model)$coefficients[1,1] +  
  summary(bp_grass_model)$coefficients[2,1] * log(PPFD$PPFD) +
  summary(bp_grass_model)$coefficients[3,1] * Tg$Tg

@@

#work on effect of each factor on NUE
#now, work on NUE
nue_final <- all_maps$NUE # by default

cal_nue <- function(Tg_pred,PPFD_pred,vpd_pred,fAPAR_pred,age_pred,CNrt_pred,LMA_pred,vcmax25_pred){
  npp_f <- summary(bp_model)$coefficients[1,1] +  
    summary(bp_model)$coefficients[2,1] * Tg_pred +
    summary(bp_model)$coefficients[3,1] * fAPAR_pred +
    summary(bp_model)$coefficients[4,1] * log(PPFD_pred) +
    summary(bp_model)$coefficients[5,1] * log(CNrt_pred)+
    summary(bp_model)$coefficients[6,1] * log(age_pred)

@@

nue_standard <- cal_nue(Tg$Tg,PPFD$PPFD,vpd$vpd,fAPAR$fAPAR,
                        age$age,CNrt$CNrt,LMA$LMA,vcmax25_df$vcmax25)
summary(nue_standard)

mean_Tg <- mean(Tg$Tg[is.na(available_grid2)==FALSE]);mean_Tg
mean_PPFD <- mean(PPFD$PPFD[is.na(available_grid2)==FALSE]);mean_PPFD
mean_vpd <- mean(vpd$vpd[is.na(available_grid2)==FALSE]);mean_vpd
mean_fAPAR <- mean(fAPAR$fAPAR[is.na(available_grid2)==FALSE]);mean_fAPAR
mean_age <- mean(age$age[is.na(available_grid2)==FALSE]);mean_age
mean_CNrt <- mean(CNrt$myvar[is.na(available_grid2)==FALSE]);mean_CNrt
mean_LMA <- mean(LMA$LMA[is.na(available_grid2)==FALSE]);mean_LMA
mean_vcmax25 <- mean(vcmax25_df$vcmax25[is.na(available_grid2)==FALSE]);mean_vcmax25

nue_Tg <- cal_nue(rep(mean_Tg,259200),PPFD$PPFD,vpd$vpd,fAPAR$fAPAR,age$age,CNrt$myvar,LMA$LMA,vcmax25_df$vcmax25)
nue_PPFD <- cal_nue(Tg$Tg,rep(mean_PPFD,259200),vpd$vpd,fAPAR$fAPAR,age$age,CNrt$myvar,LMA$LMA,vcmax25_df$vcmax25)
nue_vpd <- cal_nue(Tg$Tg,PPFD$PPFD,rep(mean_vpd,259200),fAPAR$fAPAR,age$age,CNrt$myvar,LMA$LMA,vcmax25_df$vcmax25)
nue_fAPAR <- cal_nue(Tg$Tg,PPFD$PPFD,vpd$vpd,rep(mean_fAPAR,259200),age$age,CNrt$myvar,LMA$LMA,vcmax25_df$vcmax25)
nue_age <- cal_nue(Tg$Tg,PPFD$PPFD,vpd$vpd,fAPAR$fAPAR,rep(mean_age,259200),CNrt$myvar,LMA$LMA,vcmax25_df$vcmax25)
nue_CNrt <- cal_nue(Tg$Tg,PPFD$PPFD,vpd$vpd,fAPAR$fAPAR,age$age,rep(mean_CNrt,259200),LMA$LMA,vcmax25_df$vcmax25)
nue_LMA <- cal_nue(Tg$Tg,PPFD$PPFD,vpd$vpd,fAPAR$fAPAR,age$age,CNrt$myvar,rep(mean_LMA,259200),vcmax25_df$vcmax25)
nue_vcmax25 <- cal_nue(Tg$Tg,PPFD$PPFD,vpd$vpd,fAPAR$fAPAR,age$age,CNrt$myvar,LMA$LMA,rep(mean_vcmax25,259200))

@@

# for all logit function model (mod_tnpp, mod_anpp, mod_lnpp, nre_model): a = 1/(1+exp(-b)), where a is the ratio (e.g. npp/gpp) and b is the regression (e.g. mod =tnpp)
#we calculate uncertainty of b firstly, based on each regression
#now we need to calculate deriative a / deriative b, based on a = 1/(1+exp(-b)). After calculation it is: exp(-b) / ( (1 + exp(-b)) ^2)
#forest anpp
mod_anpp_uncertainty <- summary(anpp_tnpp_model)$sigma
anpp_b <- summary(anpp_tnpp_model)$coefficients[1,1]+
  summary(anpp_tnpp_model)$coefficients[2,1] * log(CNrt$myvar) +
  summary(anpp_tnpp_model)$coefficients[3,1] * log(PPFD$PPFD) + 
  summary(anpp_tnpp_model)$coefficients[4,1] * Tg$Tg+
  summary(anpp_tnpp_model)$coefficients[5,1] * log(age$age)

@@

## Uncertainty of LNPP/ANPP
mod_lnpp_uncertainty <- summary(anpp_leafnpp_model)$sigma
lnpp_b <- summary(anpp_leafnpp_model)$coefficients[1,1]+
  summary(anpp_leafnpp_model)$coefficients[2,1]* fAPAR$fAPAR +
  summary(anpp_leafnpp_model)$coefficients[3,1] * log(vpd$vpd) + 
  summary(anpp_leafnpp_model)$coefficients[4,1] * log(PPFD$PPFD)

@@

#NRE
mod_nre_uncertainty <- summary(nre_model)$sigma
nre_b <- summary(nre_model)$coefficients[1,1]  +
  summary(nre_model)$coefficients[2,1] * Tg$Tg + summary(nre_model)$coefficients[3,1] * log(vpd$vpd)
mod_nre_uncertainty <- mod_nre_uncertainty *  exp(-nre_b) / ( (1 + exp(-nre_b)) ^2)
summary(mod_nre_uncertainty)
